Methods for Large Scale Learning to Rank

### 2014-10-24 report/Chapters/Background.tex
MAP gefixt
reduce + fold

$AP = \frac{\sum\nolimits_{k=1}^{n}Precision(k)*relevance(k)}{\text{number of relevant docs}}$\\

With $k$ being the positions in the result set between 1 and $n$. Table \ref{tab:example_calculation_AP} provides an example calculation of average precision where de documents at positions 1, 5, 6 and 8 in the ranking are relevant. The total number of available relevant documents in the document set \emph{R} is assumed to be seven.
\ac{MAP} is the average \ac{AP} for a set of queries.\\

@@

\section{An introduction to the MapReduce programming model}
MapReduce \cite{Dean2004} is a programming model invented at Google, where users specify a \emph{map} function that processes a key/value pair to generate a set of intermediate key/value pairs, and a \emph{reduce} function that merges all intermediate values associated with the same intermediate key. This model draws its inspiration from the field of functional programming, where \emph{map} and \emph{reduce} are commonly used functions.\\

>>>>

$AP(q) = \frac{\sum\nolimits_{k=1}^{n}Precision(k)*rel_k}{\text{number of relevant docs}}$\\

where $n$ is the number of documents in query $q$. Since \ac{AP} is a binary relevance judgement metric, $rel_k$ is either 1 (relevant) or 0 (not relevant). Table \ref{tab:example_calculation_AP} provides an example calculation of average precision where de documents at positions 1, 5, 6 and 8 in the ranking are relevant. The total number of available relevant documents in the document set \emph{R} is assumed to be seven. \ac{MAP} is the average \ac{AP} for a set of queries.\\

@@

\section{An introduction to the MapReduce programming model}
MapReduce \cite{Dean2004} is a programming model invented at Google, where users specify a \emph{map} function that processes a key/value pair to generate a set of intermediate key/value pairs, and a \emph{reduce} function that merges all intermediate values associated with the same intermediate key. This model draws its inspiration from the field of functional programming, where \emph{map} and \emph{reduce} (in some functional languages called \emph{fold}) are commonly used functions.\\
